A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 main.tex
Updates from Overleaf

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
$$
S_{\theta}(t)= \mathbb{P}(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
$$
\cm{where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is}
\[
	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty} t \cdot S_\theta(t) \,dt.
\]

@@

To choose a best-fit from the possible AFR functions, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}. \cm{For AIC and BIC, that means choosing the smallest value. Concordance, however, is a number between $-1$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival}. By evaluating $\mathbb{E}_{S_\theta}[T]$ for both adversarial and benign data, we can test the model under extreme perturbations and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}}

@@

\subsection{Optimisation}
\label{optimisation}
\cm{Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.} However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
making it infeasible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers}. Therefore, a proper search would keep this dual-objective in mind.
\cm{To optimize for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because of its ability to work in distributed settings,  while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}}.

@@

Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time. However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increase the attack distance by an order of magnitude reduces the survival time marginally. Additionally, we see that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.

>>>>

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
$$
S_{\theta}(t)= \mathbb{P}(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
$$
\cm{where $\mathbb{P}(T>t)$ is the probability that a model has not failed by time $t$. Then, the expected survival time is}
\[
	\mathbb{E}_{S_\theta}[T] = \int_0^{\infty}  S_\theta(t) \,dt.
\]

@@

To choose a best-fit from the possible AFR functions, one should compare Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance following the best-practices of this methodology~\cite{aft_models,kleinbaum1996survival}. \cm{For AIC and BIC, that means choosing the smallest value. Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and .5 reflects random chance. By evaluating $\mathbb{E}_{S_\theta}[T]$ for both adversarial and benign data, we can test the model under extreme perturbations and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}}

@@

\subsection{Optimisation}
\label{optimisation}
\cm{Machine learning models are typically trained across a wide variety of hyper-parameters to determine the ``best" model by minimizing an optimisation program (minimizing a loss function associated with the machine learning problem) by measuring the loss across many configurations of a model.} However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of such parameters,
making it infeasible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017}--with several researchers noting an inverse relationship between model accuracy and model robustness ~\cite{carlini_towards_2017,meyers}. Therefore, a proper search would keep this dual-objective in mind.
\cm{To optimize for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging  over tens or hundreds of trials~\cite{ozaki2020multiobjective}}.

@@

Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time. However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time. Additionally, that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.
